Functional oxide layers for electrical isolation and chemical passivation of steel substrates

### 2022-10-16 Thesis/chapter/03-theoretical-background.tex
sputter figure version 0

%\td{how does it work?}\\
A high voltage is applied to 
two parallel electrodes with low pressure gas in between. 
The target acts as cathode and the substrate (holder) as anode (see \td{fig}).
%the target which acts as a cathode with the substrate as anode in a parallel geometry (see \td{fig}).
The cathode, then, emits electrons which collide with a gas particles (mostly argon because of it's inert properties and potential to transfer more kinetic than lighter noble gases). 
Some gas particles may get ionized by the collision and the gas cations are accelerated to the cathode. 
If a cation has enough energy it will bump off one or more atoms or molecules from the surface. 
This happens by a cascade of momentum transfers, which can reach the surface again (see fig \td{cp sigmund69}). 
If a surface particle obtains momentum pointing away from the bulk and its kinetic energy is higher than the binding energy, the particle is sputtered. 
This sputtered particle travels unaffected by the electrical field perpendicular to the surface towards the substrate and condenses with other particles to form a layer.
The pressure should be small, such that the sputtered particle has a long \gls{mfp}, but on the other hand 
a minimum pressure is needed to keep the plasma "alive". 
Usual pressures are around \SI{1}{\Pa} (\num{e-2}\SI{}{\milli\bar}) or lower\cite{Swann1988}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Infrared Absorption and Spectroscopy}
%%% WHAT? 
\Gls{ir} spectroscopy is a molecular spectroscopic method using interactions of \gls{ir} light (wavelengths $\lambda$ of \num{e-3} to \num{e-6}\m{}
or wave numbers $\bar{\nu}$ of 500 to \pcm{4000} ) with molecules. \cite{Schwedt2008}
In general, light is described as periodic \gls{em} wave 
which - in vacuum - moves with the speed of light ($c = \mps{299792458}$).
The relation of energy~$E$ of a photon, its frequency~$\nu$, wavelength~$\lambda$ and wave number~$\bar{\nu}$ are as follows:
\begin{align*}
	E &= h \cdot \nu \\
	\nu &= c/ \lambda \\
	\bar{\nu} &= 1/\lambda,
\end{align*}
where $h$ is the Planck's constant.
%In words: shorter wavelength (higher frequency) photons are more energetic.
In practice the spectrum of \gls{em} waves is sectioned into different ranges (\td{see figure?});
from high to low energy: X-ray, \gls{uv}, \gls{vis}, (near, middle and far) \gls{ir}, microwaves and radio waves. 
\td{with number?}
X-rays interact with core electrons, \gls{uv}\gls{vis} with valence electrons, \gls{ir} with molecular vibrations, microwaves with molecular rotations and radio with electron and nuclear spins. 
%Molecular vibrations can be separated in valence and deformation vibrations.
%
A molecule has $F=3N$ ($N$ number of atoms) degrees of freedom, including translational $F_T=3$ and rotational $F_R=3$ (2 for linear molecules) movements. 
%
The number of vibrations can therefore calculated as 
\begin{align*}
	F_V &= 3N - F_T - F_R = 3N - 6 \\
	F_V &= 3N - F_T - F_R = 3N - 5 \textrm{ (for linear molecules)}.
\end{align*}
Vibrations are classified in valence vibrations (change of bond length) and deformation (change of bond angle) vibrations\cite{Melker2006}. 
Only vibrations that change the dipole moment of the molecule are \gls{ir} active.

@@

\paragraph{(Fourier Transform) Infrared spectrometer}
 A ceramic material (Nernst glower) is heated to around \oc{1600} as light source. 
 In the two-beam-spectrometer the light is split, sent through the sample and a reference and one of the two beams is alternately sent through a monochromator to a detector (\td{thermocouple}). 
%
In the \gls{ft}\gls{ir} spectrometer the beam is sent through the sample, split and 
reflected from a static and from a moving mirror, recombined and detected by a photo 
multiplier (a device which transforms photons into electrical signals). 
How the two beams will interfere upon recombination depends on the optical path difference (also called retardation) of the two light beams\cite{Schwedt2008}.
In a \gls{ft}\gls{ir} spectrometer the reference has to be measured before the sample.
%
When the refractive index of two layers differ, \gls{ir} can be used to measure the thickness\cite{Dumin1967} of optical less dense material.

@@

\td{QUESTIONS: 
	how does detector work? two different for UVVis and MIR
	IR around page 45;
The absorbance intensity is dependent on wave length and molecule structure. 
Absorbance per din 1349: $A(\lambda) = \log{\frac{\phi_{in}}{\phi_{ex}}}$ and transmission $\tau =T=D= \phi_{ex}/\phi_{in}$
}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Artificial Inteligence and Machine Learning}
%How can \gls{ai} and \gls{ml} be defined? 
\Gls{ai} is a trans-disciplinary field with roots in logic, statistics, cognitive psychology, decision theory, neuroscience, linguistics, cybernetics, and computer engineering.\cite{howard2019artificial}
The history of \gls{ai} goes back to the middle of the \nth{20} century. 
Researchers from the emerging field came together at the Dartmouth conference and the term "\gls{ai}" was coined\cite{McCarthy1955}. 
\Gls{ai}'s  history is beautifully depicted by McCorducks' 1982 book "Machines Who Think"\cite{McCorduck1982,Apter1982}, which focuses on the great minds behind the advances.
Pioneers like Alan Turing thought a lot about how to define, test and implement \gls{ai}\cite{howard2019artificial}. 
One example how to measure \gls{ai} is to let it play chess against a human\cite{Silver2017} 
(in 1997 a chess computer called Deep Blue won against the World Chess Champion Garry Kasparov for the first time\cite{Feng1999}).
%Another test ingenioused by Alan Turing, is that a human communicates with an unknown entity (in written form) and must judge if they are dealing with a machine or a human being. 
Another test ingenioused by Alan Turing, is the imitation game\cite{turing1950imitation}, now a days known as Turing test.
An interrogator communicates with two unknown entities \textbf{A} and \textbf{B} (a woman and a man) and must find out who is who. 
\textbf{A} will try to make to interrogator misjudge, whereas \textbf{B} is in the interrogators side.
The question is if \textbf{A} is replaced with an computer how the ratio of outcomes would deviate from the original ratio. 
%
%(in written form) and must judge who is the 
%if they are dealing with a machine or a human being. 
%
\td{It is easy for humans to come up with question to detect an AI, 
but when reading AI written articles\cite{gpt2020}, it's easy to see this test being passed in the near future.}

@@

%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Machine Learning Methods}
%
\Gls{ml} is at the base of most \gls{ai}s.
It is an umbrella term for programs with instructions to learn from data, i.e. gain knowledge, categorise, predict and make decisions based on data. 
%
There is a platitude of different machine learning methods: 
they can be divided into supervised (training set is labeled) and unsupervised (exploratory).  
An orthogonal division can be made by regression (continuous data) versus classification (discrete, categorical data). 
%Two architecture which don't quite fit into this classification are Generative Adversarial Network (GAN) and jk
Independent from these $2\times2$ categories there are multiple ways to let machines learn from data.
%
\Gls{nn} (one of the most popular architectures for big data\cite{Chiroma2019}) are loosely modeled after the brain\cite{bishop1994neural}.
Artificial neurons (also called nodes), which are arranged in layers, 
are connected to each of the neurons of previous and next layers
and the weights (parameters of intensity), with which the data is routed from one neuron to another, 
are optimised during training. 
%
Convolutional-layer \gls{nn} excel in picture recognition\cite{Lecun1995conv} and in quantum mechanics too\cite{westermayr2020combining}.
Other common architectures include linear regression, kernel ridge regression and support vector regression.
There are also lesser know algorithms like 
evolutionary algorithms (e.g. \gls{ga} and \gls{pso}).
%
One advantage of evolutionary algorithms is that they start with a small data set
and periodically request new data in order to solve the problem iteratively.
\td{This is exactly what I needed because every experiment is very time intensive.}

>>>>

\begin{figure}[htb]
	\includegraphics[width=\textwidth]{./Pics/sputter0.png}
    \caption{Propagation of energy in a dense cascade. Left graph: "Primary" shockwave. Right graph: "Thermal" pulse or "secondary" shockwave. Figure taken from Sigmund 1987\cite{sigmund1987}}
	\label{fig:sputter}
\end{figure}

%\td{how does it work?}\\
A high voltage is applied to 
two parallel electrodes with low pressure gas in between. 
The target acts as cathode and the substrate (holder) as anode (see figure \ref{fig:sputter}).
%the target which acts as a cathode with the substrate as anode in a parallel geometry (see \td{fig}).
The cathode, then, emits electrons which collide with a gas particles (mostly argon because of it's inert properties and potential to transfer more kinetic than lighter noble gases). 
Some gas particles may get ionized by the collision and the gas cations are accelerated to the cathode. 
If a cation has enough energy it will bump off one or more atoms or molecules from the surface. 
This happens by a cascade of momentum transfers, which can reach the surface again (see fig \td{from \cite{sigmund1987}}). 
If a surface particle obtains momentum pointing away from the bulk and its kinetic energy is higher than the binding energy, the particle is sputtered. 
This sputtered particle travels unaffected by the electrical field perpendicular to the surface towards the substrate and condenses with other particles to form a layer.
The pressure should be small, such that the sputtered particle has a long \gls{mfp}, but on the other hand 
a minimum pressure is needed to keep the plasma "alive". 
Usual pressures are around \SI{1}{\Pa} (\num{e-2}\SI{}{\milli\bar}) or lower\cite{Swann1988}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Infrared Absorption and Spectroscopy}
%%% WHAT? 
\Gls{ir} spectroscopy is a molecular spectroscopic method using interactions of \gls{ir} light (wavelengths $\lambda$ of \num{e-3} to \num{e-6}\m{}
or wave numbers $\bar{\nu}$ of 500 to \pcm{4000} ) with molecules. \cite{Schwedt2008}
In general, light is described as periodic \gls{em} wave 
which - in vacuum - moves with the speed of light ($c = \mps{299792458}$).
The relation of energy~$E$ of a photon, its frequency~$\nu$, wavelength~$\lambda$ and wave number~$\bar{\nu}$ are as follows:
\begin{align*}
	E &= h \cdot \nu \\
	\nu &= c/ \lambda \\
	\bar{\nu} &= 1/\lambda,
\end{align*}
where $h$ is the Planck's constant.
%In words: shorter wavelength (higher frequency) photons are more energetic.
In practice the spectrum of \gls{em} waves is sectioned into different ranges (\td{see figure?+table});
from high to low energy: X-ray, \gls{uv}, \gls{vis}, (near, middle and far) \gls{ir}, microwaves and radio waves. 
X-rays interact with core electrons, \gls{uv}\gls{vis} with valence electrons, \gls{ir} with molecular vibrations, microwaves with molecular rotations and radio with electron and nuclear spins. 
%Molecular vibrations can be separated in valence and deformation vibrations.
%
A molecule has $F=3N$ ($N$ number of atoms) degrees of freedom, including translational $F_T=3$ and rotational $F_R=3$ (2 for linear molecules) movements. 
%
The number of vibrations can therefore calculated as 
\begin{align*}
	F_V &= 3N - F_T - F_R = 3N - 6 \\
	F_V &= 3N - F_T - F_R = 3N - 5 \textrm{ (for linear molecules)}.
\end{align*}
Vibrations are classified in valence vibrations (change of bond length) and deformation (change of bond angle) vibrations\cite{Melker2006}. 
Only vibrations that change the dipole moment of the molecule are \gls{ir} active.

@@

\paragraph{(Fourier Transform) Infrared spectrometer}
 A ceramic material (Nernst glower) is heated to around \oc{1600} as light source. 
 In the two-beam-spectrometer the light is split, sent through the sample and a reference and one of the two beams is alternately sent through a monochromator to a detector (often a thermopile).
%
In the \gls{ft}\gls{ir} spectrometer the beam is sent through the sample, split and 
reflected from a static and from a moving mirror, recombined and detected by a photo 
multiplier (a device which transforms photons into electrical signals). 
How the two beams will interfere upon recombination depends on the optical path difference (also called retardation) of the two light beams\cite{Schwedt2008}.
In a \gls{ft}\gls{ir} spectrometer the reference has to be measured before the sample.
%
When the refractive index of two layers differ, \gls{ir} can be used to measure the thickness\cite{Dumin1967} of optical less dense material.

@@

\td{
	IR around page 45;
The absorbance intensity is dependent on wave length and molecule structure. 
Absorbance per din 1349: $A(\lambda) = \log{\frac{\phi_{in}}{\phi_{ex}}}$ and transmission $\tau =T=D= \phi_{ex}/\phi_{in}$
}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Artificial Inteligence and Machine Learning}
%How can \gls{ai} and \gls{ml} be defined? 
\Gls{ai} is a trans-disciplinary field with roots in logic, statistics, cognitive psychology, decision theory, neuroscience, linguistics, cybernetics, and computer engineering.\cite{howard2019artificial}
The history of \gls{ai} goes back to the middle of the \nth{20} century. 
Researchers from the emerging field came together at the Dartmouth conference and the term "\gls{ai}" was coined\cite{McCarthy1955}. 
\Gls{ai}'s  history is beautifully depicted by McCorducks' 1982 book "Machines Who Think"\cite{McCorduck1982,Apter1982}, which focuses on the great minds behind the advances.
Pioneers like Alan Turing thought a lot about how to define, test and implement \gls{ai}\cite{howard2019artificial}. 
One example how to measure \gls{ai} is to let it play chess against a human\cite{Silver2017} 
(in 1997 a chess computer called Deep Blue won against the World Chess Champion Garry Kasparov for the first time\cite{Feng1999}).
%Another test ingenioused by Alan Turing, is that a human communicates with an unknown entity (in written form) and must judge if they are dealing with a machine or a human being. 
Another test ingenioused by Alan Turing, is the imitation game\cite{turing1950imitation}, now a days known as Turing test.
An interrogator communicates with two unknown entities \textbf{A} and \textbf{B} (a woman and a man) and must find out who is who. 
\textbf{A} will try to make to interrogator misjudge, whereas \textbf{B} is on the interrogators side.
The question is if \textbf{A} is replaced with a computer how the ratio of outcomes would deviate from the original ratio. 
%
%(in written form) and must judge who is the 
%if they are dealing with a machine or a human being. 
%
%
%\ds{It is easy for humans to come up with question to detect an AI, 
%but when reading AI written articles\cite{gpt2020}, 
%it's easy to see this test being passed in the near future.}
%
At the moment it's hard to imagine a computer getting a higher ratio than a human
but when reading AI written articles\cite{gpt2020}, it's easy to see this test being passed in the future.

@@

%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Machine Learning Methods}
%
\Gls{ml} is at the base of most \gls{ai}s.
It is an umbrella term for programs with instructions to learn from data, i.e. gain knowledge, categorise, predict and make decisions based on data. 
%
There is a platitude of different machine learning methods: 
they can be divided into supervised (training set is labeled) and unsupervised (exploratory).  
An orthogonal division can be made by regression (continuous data) versus classification (discrete, categorical data). 
%Two architecture which don't quite fit into this classification are Generative Adversarial Network (GAN) and jk
Independent from these $2\times2$ categories there are multiple ways to let machines learn from data.
%
\Gls{nn} (one of the most popular architectures for big data\cite{Chiroma2019}) are loosely modeled after the brain\cite{bishop1994neural}.
Artificial neurons (also called nodes), which are arranged in layers, 
are connected to each of the neurons of previous and next layers
and the weights (parameters of intensity), with which the data is routed from one neuron to another, 
are optimised during training. 
%
Convolutional-layer \gls{nn} excel in picture recognition\cite{Lecun1995conv} and in quantum mechanics too\cite{westermayr2020combining}.
Other common architectures include linear regression, kernel ridge regression and support vector regression.
There are also lesser know algorithms like 
evolutionary algorithms (e.g. \gls{ga} and \gls{pso}).
\gls{pso} algorithms take advantage of the ability to cope with local optima by evolving several candidate solutions simulta- neously\cite{Villannova2010}.
%
One advantage of evolutionary algorithms is that they start with a small data set
and periodically request new data in order to solve the problem iteratively.
\td{This is exactly what I needed because every experiment is very time intensive.}
